Replication Survey

### 2023-09-28 docs/manuscript/manuscript.tex

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature. 
We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Data Collection}
We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between May 17 and June 10, 2022.
A simple random sample of 2,000 researchers was drawn without replacement from our sampling frame, and those researchers were invited via email to participate in the online survey. 
Researchers received their initial invitation on May 17, 2022. 
Two reminder emails were sent to researchers that had not yet completed the survey on May 26 and May 31, 2022.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure A). 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
In particular, respondents believe that replication studies can be used to assess the construct validity (75\%) and external validity of a prior study.
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

\begin{center}
\textbf{Insert Figure A About Here}
\end{center}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.5]{results/figures/Fig-Q12-HCS.png}
    \caption{Estimates of the percentage of geographic studies that (a) have been replicated, (b) could be replicated, or (c) should be replicated}
    \label{fig:Q12-HCS}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of no effect (NE), `don't know' (DK), and missing (M) responses.}
    \label{fig:Q8-10-Chances}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
    \label{fig:Q15-DecisionFactors}
\end{figure}

>>>>

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature. 
We pilot tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Data Collection}
We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between Oct 3 and Oct 27, 2022.
A simple random sample of 2,000 researchers was drawn without replacement from our sampling frame, and those researchers were invited via email to participate in the online survey. 
Researchers received their initial invitation on Oct 3, 2022. 
Two reminder emails were sent to researchers that had not yet completed the survey on Oct 13 and Oct 20, 2022.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure \ref{fig:Q7-Epistemology}). 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
In particular, respondents believe that replication studies can be used to assess the construct validity (75\%) and external validity of a prior study.
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

\begin{center}
\textbf{Insert Figure \ref{fig:Q7-Epistemology} About Here}
\end{center}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=1]{results/figures/Fig1-Q7-Epistemology.png}
    \caption{Perceptions of the epistemological function of replication studies. Respondents identified the extent to which they agree replication studies can be used to assess the claims or features of past research; `don't know' (DK), and missing (M) responses.}
    \label{fig:Q7-Epistemology}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.5]{results/figures/Fig2-Q12-HCS.png}
    \caption{Estimates of the percentage of geographic studies that (a) have been replicated, (b) could be replicated, or (c) should be replicated}
    \label{fig:Q12-HCS}
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.8]{results/figures/Fig3-Q8-10-Chances.png}
    \caption{Factors affecting the chances of replicating a study. Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location. Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of no effect (NE), `don't know' (DK), and missing (M) responses.}
    \label{fig:Q8-10-Chances}
\end{figure}

\begin{figure}[hbt!]
    \centering
    \includegraphics[scale=0.80]{results/figures/Fig4-Q15-Decisions.png}
    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
    \label{fig:Q15-DecisionFactors}
\end{figure}
